IFA Comparison of Noncognitive Skills \\ BCS and MCS

### 2018-04-10 codes/R/cohorts_nc.Rnw
add tables to quantify gradients (M and F)

For ease of interpretation, I choose to rescale the factor loadings using \emph{oblimin} rotation: this method allows the underlying factors to be correlated to each other. From the results of the exploratory FA and IRT analysis with 2 factors, the pattern that seems to emerge is consistent with the theoretical constructs of externalising (EXT) and internalising (INT) behaviour problems.

<<BCSEFA>>=
@
% 
% <<BCSEFARES, dependson='BCSEFA', echo=T, results='markup'>>=
% @

@@

<<MCSEFA>>=
@
% 
% # <<MCSEFARES, dependson='BCSEFA', echo=T, results='markup'>>=
% # @
%

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage
% THIS BREAKS THE CACHING FOR SOME REASON
% <<IQRDEC_FUN>>=
% # load functions
% @
% 
% <<IQRDEC, dependson="FA_SCORES_MAIN">>=
% # decompose
% @
% 
% % Compare inequality statistics of original vs residualised scores
% % <<IQRDEC_RES, dependson='IQRDEC', echo=T, results='markup'>>=
% % iqs.orig
% % iqs.resid
% % @

@@

<<COUNTERF, dependson="FA_SCORES_MAIN">>=
# perform counterfactuals
@

<<COUNTERF_PREP_PLOTS, dependson='COUNTERF'>>=
# prepare counterfactual plots
@

\begin{landscape}
\begin{figure}
<<COUNTERF_EXT, dependson='COUNTERF_PREP_PLOTS', dev='tikz', fig.height=10, fig.width=16, out.width='1\\linewidth'>>=
cfp.ext
@
\caption{Counterfactual decomposition -- externalising skills}\label{fig:counterf}
{\scriptsize \emph{Notes}: \par}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
<<COUNTERF_INT, dependson='COUNTERF_PREP_PLOTS', dev='tikz', fig.height=10, fig.width=16, out.width='1\\linewidth'>>=
cfp.int
@
\caption{Counterfactual decomposition -- internalising skills}\label{fig:counterf}
{\scriptsize \emph{Notes}: \par}
\end{figure}
\end{landscape}

>>>>

For ease of interpretation, I choose to rescale the factor loadings using \emph{oblimin} rotation: this method allows the underlying factors to be correlated to each other. From the results of the exploratory FA and IRT analysis with 2 factors, the pattern that seems to emerge is consistent with the theoretical constructs of externalising (EXT) and internalising (INT) behaviour problems.
% 
% <<BCSEFA>>=
% @
% 
% <<BCSEFARES, dependson='BCSEFA', echo=T, results='markup'>>=
% @

@@

% 
% <<MCSEFA>>=
% @
% 
% # <<MCSEFARES, dependson='BCSEFA', echo=T, results='markup'>>=
% # @
%

@@

\clearpage
\begin{figure}
\begin{center}
<<INCINEQ, dependson="FA_SCORES_MAIN", dev='tikz', fig.height=4, fig.width=4, out.width='.5\\linewidth'>>=
@
\end{center}
\caption{Evolution of income inequality }
{\scriptsize \emph{Notes}:  \par}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage

<<DEC_VARS>>=
# define variables for decomposition
@
% 
% !!!!!!!!!! THIS BREAKS CACHING !!!!!!!!!!!!!!!!!!!!!
% <<DEC_IQR, dependson="DEC_VARS">>=
% # decompose SD and IQRs
% @
% 
% Compare inequality statistics of original vs residualised scores
% <<DEC_RES, dependson='DEC_IQR', echo=T, results='markup'>>=
% iqs.orig
% iqs.resid
% @

\begin{table}
\caption{Quantifying the gradient -- males}
\centering
<<FA_REGS_REAL_M, dependson='DEC_VARS', results='asis'>>=
# regress scores on income
library(dplyr)
library(stargazer)

r.ext.m.bcs <- lm(form.ext, data=subset(scores2plot, sex=="M" & cohort=="BCS"))
r.ext.m.mcs <- lm(form.ext, data=subset(scores2plot, sex=="M" & cohort=="MCS"))
r.int.m.bcs <- lm(form.int, data=subset(scores2plot, sex=="M" & cohort=="BCS"))
r.int.m.mcs <- lm(form.int, data=subset(scores2plot, sex=="M" & cohort=="MCS"))

stargazer(r.ext.m.bcs, r.ext.m.mcs , r.int.m.bcs, r.int.m.mcs, #r.ext.f.bcs, r.ext.f.mcs , r.int.f.bcs, r.int.f.mcs,
          column.labels=c("BCS M","MCS M","BCS M","MCS M"), #,"BCS F","MCS F","BCS F","MCS F"),
          dep.var.caption = "", multicolumn = FALSE,
          omit=c("Constant", paste0("region", c(2:9))),
          # covariate.labels=c(
          #                    "Income Q2",
          #                    "Income Q3",
          #                    "Income Q4",
          #                    "Income Q5"
          #                    ),
          no.space=TRUE,
          omit.stat= c("rsq", "f", "ser", "aic", "ll"),
          notes = "All estimates control for Government Office Region of birth.",
          float=FALSE    # needs begin table outside it
)
@
\end{table}

\begin{table}
\caption{Quantifying the gradient -- females}
\centering
<<FA_REGS_REAL_F, dependson='DEC_VARS', results='asis'>>=
# regress scores on income
library(dplyr)
library(stargazer)

r.ext.m.bcs <- lm(form.ext, data=subset(scores2plot, sex=="F" & cohort=="BCS"))
r.ext.m.mcs <- lm(form.ext, data=subset(scores2plot, sex=="F" & cohort=="MCS"))
r.int.m.bcs <- lm(form.int, data=subset(scores2plot, sex=="F" & cohort=="BCS"))
r.int.m.mcs <- lm(form.int, data=subset(scores2plot, sex=="F" & cohort=="MCS"))

stargazer(r.ext.m.bcs, r.ext.m.mcs , r.int.m.bcs, r.int.m.mcs, #r.ext.f.bcs, r.ext.f.mcs , r.int.f.bcs, r.int.f.mcs,
          column.labels=c("BCS F","MCS F","BCS F","MCS F"), #,"BCS F","MCS F","BCS F","MCS F"),
          dep.var.caption = "", multicolumn = FALSE,
          omit=c("Constant", paste0("region", c(2:9))),
          # covariate.labels=c(
          #                    "Income Q2",
          #                    "Income Q3",
          #                    "Income Q4",
          #                    "Income Q5"
          #                    ),
          no.space=TRUE,
          omit.stat= c("rsq", "f", "ser", "aic", "ll"),
          notes = "All estimates control for Government Office Region of birth.",
          float=FALSE    # needs begin table outside it
)
@
\end{table}

@@

% 
% <<COUNTERF, dependson="FA_SCORES_MAIN">>=
% # perform counterfactuals
% @
% 
% <<COUNTERF_PREP_PLOTS, dependson='COUNTERF'>>=
% # prepare counterfactual plots
% @
% 
% \begin{landscape}
% \begin{figure}
% <<COUNTERF_EXT, dependson='COUNTERF_PREP_PLOTS', dev='tikz', fig.height=10, fig.width=16, out.width='1\\linewidth'>>=
% cfp.ext
% @
% \caption{Counterfactual decomposition -- externalising skills}\label{fig:counterf}
% {\scriptsize \emph{Notes}: \par}
% \end{figure}
% \end{landscape}
% 
% \begin{landscape}
% \begin{figure}
% <<COUNTERF_INT, dependson='COUNTERF_PREP_PLOTS', dev='tikz', fig.height=10, fig.width=16, out.width='1\\linewidth'>>=
% cfp.int
% @
% \caption{Counterfactual decomposition -- internalising skills}\label{fig:counterf}
% {\scriptsize \emph{Notes}: \par}
% \end{figure}
% \end{landscape}
